You can follow this tutorial on making your own package in R:
https://hilaryparker.com/2014/04/29/writing-an-r-package-from-scratch/


*Install and load the two packages needed to get started
```{r}
install.packages("devtools")
library(devtools)
devtools::install_github("klutometis/roxygen")
library(roxygen2)
install.packages("svDialogs")
library(svDialogs)
```

*Create package directory where you will save your package
```{r}
mydir <- dlg_input("Provide the directory path where you would like to create a new package:")$res
setwd(mydir)

packageName <- dlg_input("Provide the name you would like to give your new package")$res
create(packageName)
```

*Edit the description file that now appears in your directory, inside the folder with your package name.
  You should include your contact information, a title, description of the purpose, etc. 

*Save your function to an R file in the same folder, and include a header with commented out information
Ex:
#' Function Title
#'
#' This function allows you to ...
#' @param paramName [short description of the param]
#' @keywords [keywords related to your function]
#' @export
#' @examples
#' function_name()

*Process your documentation
```{r}
setwd(paste0(mydir, "/", packageName))
document()
```

*Install your new package and test 
```{r}
install(packageName) # install
library(paste(packageName), character.only = TRUE) # load the library

?... # insert the name of a function and view help file
```


*Put your package on github, and then test installation from there:
  ex: the repository path is username/folder/subfolder
```{r}
repo <- dlg_input("Provide the github repository path where your package is stored:")$res
install_github(repo)
```

 